Questions to Developers

### 2020-10-29 StateOfPractice/Methodology/Questions to Developers.tex
added comment about pilot into Questions to Developers
updated quesiton 10 an added comments into Questions to Developers

\maketitle

\section{Information about the developers and users}\citep{Jegatheesan2016}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item Do you have a defined process for accepting new contributions into your team?
\item What is the typical background of a developer?
\item What is your estimated number of users? How did you come up with that estimate?
\item What is the typical background of a user?
\end{enumerate}

@@

\begin{enumerate}
\item Currently, what are the most significant obstacles in your development
process?
\item How might you change your development process to remove or reduce these
obstacles?
\item How does documentation fit into your development process? Would improved
documentation help with the obstacles you typically face?
\item In the past, is there any major obstacle to your development process that
has been solved? How did you solve it?
\item What is your software development model? For example, waterfall, agile, etc.
\item What is your project management process? Do you think improve this process
can tackle the current problem? Were any project management tools used?
\item \sout{Can you name several software qualities that are the most important to
this project?}
\item Was it hard to ensure the correctness of the software? If there were any
 obstacles, what methods have been considered or practiced to improve the situation?
  If practiced, did it work?
\item When designing the software, did you consider the ease of future changes?
 For example, will it be hard to change the structure of the system, modules or code
  blocks? What measures have been taken to ensure the ease of future changes
   and maintains?
\item Do you think the users can understand your software well? Has there been
any problem to use this software?
\item Do you think the current documentation can clearly convey all necessary
knowledge to the users? If yes, how did you successfully achieve it? If no, what
improvements are needed?
\item Do you have any concern that your computational results won't be
reproducible in the future? Have you taken any steps to ensure reproducibility?
\end{enumerate}

>>>>

\maketitle
\pmi{A pilot will be conducted with these questions in order to test them. Test subjects may include PhD students.}
\section{Information about the developers and users}\citep{Jegatheesan2016}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item Do you have a defined process for accepting new contributions into your team?
\item What is the typical background of a developer?
\item What is your estimated number of users? How did you come up with that estimate?
\item What is the typical background of a user?
\end{enumerate}

@@

\pmi{consider adding `What, if any, actions were taken to address x?' to most/all questions, similar to question 10}
\pmi{questions 1,3,4,5,6 build to visibility/transparency but a question would need to be modified to include something along the line of `has this information been added to the documentation?' or as above asking about actions}
\begin{enumerate}
\item Currently, what are the most significant obstacles in your development
process? [visibility/transparency]
\item How might you change your development process to remove or reduce these
obstacles?
\item How does documentation fit into your development process? Would improved
documentation help with the obstacles you typically face? [traceability, visibility/transparency]
\item In the past, is there any major obstacle to your development process that
has been solved? How did you solve it? [visibility/transparency]
\item What is your software development model? For example, waterfall, agile, etc. [visibility/transparency]
\item What is your project management process? Do you think improve this process
can tackle the current problem? Were any project management tools used? [visibility/transparency]
\item \sout{Can you name several software qualities that are the most important to
this project?}
\item Was it hard to ensure the correctness of the software? If there were any
 obstacles, what methods have been considered or practiced to improve the situation? If practiced, did it work? [correctness]
\item When designing the software, did you consider the ease of future changes?
 For example, will it be hard to change the structure of the system, modules or code blocks? What measures have been taken to ensure the ease of future changes and maintains? [maintainability, modifiability]
\item Provide instances where users have misunderstood the software. What, if any, actions were taken to address usability issues? [usability, understandability] \pmi{should this be split into two questions?}
\item Do you think the current documentation can clearly convey all necessary
knowledge to the users? If yes, how did you successfully achieve it? If no, what
improvements are needed? [unambiguity]
\item Do you have any concern that your computational results won't be
reproducible in the future? Have you taken any steps to ensure reproducibility? [reproducibility]
\end{enumerate}
